\documentclass[10pt]{article}
\usepackage[letterpaper,
top=0.5in,
bottom=0.5in,
left=0.5in,
right=0.5in]{geometry}

\usepackage{XCharter}               % Professional serif font
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{setspace}

\raggedright
\pagestyle{empty}
\input{glyphtounicode}
\pdfgentounicode=1

% Format section headings
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{2pt}\titlerule\vspace{-5pt}]

% Format bullet points
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-1pt, leftmargin=12pt, topsep=2pt}

% Resume starts here
\begin{document}

% Name
\centerline{\Huge \textbf{Lorenzo Vecchietti}}

\vspace{5pt}

% Contact information
\centerline{\href{mailto:lorenzo.vecchietti.1997@gmail.com}{lorenzo.vecchietti.1997@gmail.com} | \href{https://github.com/lorenzovecchietti}{github.com/lorenzovecchietti} | Milan, IT}

\vspace{-5pt}

% Skills section
\section*{Skills}
\textbf{Programming:} Python \textit{(Pandas, NumPy, PyTorch, PyAnsys, FEniCSx)}, C++, SQL, Bash, Git/GitHub \\
\textbf{Simulation \& CAE:} Abaqus, OpenFOAM, Paraview, Ansys Fluent, Ansys Icepak, Ansys Mechanical \\
\textbf{Core Competencies:} CFD, FEA, Thermal Management, Numerical Optimization, Machine Learning for Physics (SimAI)

\vspace{-5pt}

% Honors & Awards section
\section*{Honors \& Awards}
\textbf{Ansys LLM Hackathon}, \textit{1st Place} -- Built an automated video suggestion engine via internal docs \& YouTube. \hfill 2024 \\
\textbf{Ansys Best Application Engineer}, Quarterly award recognizing top performance across the EMEA region. \hfill 2024 \\
\textbf{Ansys Hackathon}, \textit{2nd Place} -- Developed an AI-driven automatic post-processing tool. \hfill 2023 \\
\textbf{Alta Scuola Politecnica Scholarship}, Awarded to top 1\% of M.S. students across PoliMi and PoliTo. \hfill 2020 \\
\textbf{Best Freshmen Award}, Recognition for top-ranking first-year students at Politecnico di Milano. \hfill 2017 \\

\vspace{-5pt}

% Experience section
\section*{Experience}
\textbf{Senior Application Engineer,} \href{https://www.ansys.com/}{Ansys} -- Milan, IT \hfill Jan. 2026 -- Present\\
\textbf{Application Engineer II,} \href{https://www.ansys.com/}{Ansys} -- Milan, IT \hfill Feb. 2024 -- Jan. 2026\\
\textbf{Application Engineer,} \href{https://www.ansys.com/}{Ansys} -- Milan, IT \hfill Sept. 2022 -- Feb. 2024 \\
\vspace{-4pt}
{\setstretch{0.8}
\begin{itemize}
  \item \textbf{PyAEDT Core Contributor:} Expanded open-source Icepak coverage from $\sim$30\% to \textbf{$\sim$95\%}, enabling advanced automation for enterprise clients.
  \item \textbf{HPC \& UX Design:} Developed a custom LAPACK solution achieving a \textbf{10x speedup}; managed UX to directly influence a multi-million euro deal. Secured account renewal for a top-3 EMEA client by salvaging a critical project via custom Python automation.
  \item \textbf{AI Innovation:} Spearheading SimAI application engineering for electro-thermal management, integrating Deep Learning with physics simulation.
\end{itemize}
}

\textbf{FEA Engineer,} \href{https://www.pirelli.com/tyres/}{Pirelli} -- Milan, IT \hfill Feb. 2022 -- Aug. 2022 \\
\vspace{-5pt}
{\setstretch{0.9}
\begin{itemize}
  \item \textbf{Advanced Simulation:} Conducted complex tire behavior analysis for F1, Rally, and GT championships, directly impacting performance strategies.
  \item \textbf{Process Automation:} Architected Python scripts to automate pre-processing, reducing manual data entry time by \textbf{3x} and eliminating human error.
  \item \textbf{Infrastructure Optimization:} Diagnosed and resolved longstanding HPC queuing logic bottlenecks, increasing cluster throughput.
  \item \textbf{R\&D Implementation:} Successfully validated and field-tested a custom proprietary mesher for production workflows.
\end{itemize}
}

\vspace{-5pt}

% Education section
\section*{Education}
\textbf{\href{https://www.asp-poli.it/}{Alta Scuola Politecnica}} -- Milan/Turin, IT \hfill 2019 -- 2021 \\
Elite double-degree program for top 1\% of students focusing on multidisciplinary innovation models. \\
\textbf{\href{https://www.polimi.it/}{Politecnico di Milano}} -- M.S. in Aeronautical Engineering \hfill 2021 \\
Grade: 110/110 with Honors. Specialization: Turbulence, Numerical Methods, Optimization. \\
\textbf{\href{https://www.polimi.it/}{Politecnico di Milano}} -- B.S. in Aerospace Engineering \hfill 2019 \\
Grade: 110/110 with Honors.

\vspace{-5pt}

% Projects section
\section*{Key Projects}
\textbf{STLIMB (Master Thesis)} \hfill \href{https://github.com/lorenzovecchietti/DNSimb}{\underline{GitHub Code}} \\
\vspace{-5pt}
{\setstretch{0.9}
\begin{itemize}
  \item Developed a high-performance CFD solver based on the Immersed Boundary Method.
  \item \textbf{Impact:} Outperformed standard OpenFOAM implementations with a \textbf{25x speedup} and \textbf{70\% reduction} in memory usage.
\end{itemize}
}

\vspace{-5pt}

\section*{Extracurricular Activities}
\textbf{Aerodynamic \& CFD Engineer,} \href{https://www.dynamisprc.com/}{Dynamis PRC} (Formula Student) \hfill 2017 -- 2020 \\
\vspace{-5pt}
{\setstretch{0.9}
    \begin{itemize}
        \item Implemented advanced CFD techniques (SAS, Moving Mesh, Porous Media), contributing to multiple wins in FSAE Design Challenges.
        \item Standardized team simulation workflows, enabling cloud-based collaboration and securing sponsorships with SimScale and Lenovo.
    \end{itemize}
}

\end{document}